(working title) Local Physiological Adaptation in \textit{Mimulus cardinalis}

### 2015-04-24 ms/ms.Rnw
Small changes

  # The path to the ms directory may need to be changed for different users
  # Manuscript files
  pathMS <- "~/Google Drive/CardLocalAdaptation/ms" # Chris' MacBook
  pathMS <- "~/Documents/CardAdapt/ms" # Chris' Linux laptop

>>>>

  # The path to the ms directory may need to be changed for different users
  # Manuscript files
  pathMS <- "~/Google Drive/CardLocalAdaptation/ms" # Chris' MacBook
  # pathMS <- "~/Documents/CardAdapt/ms" # Chris' Linux laptop
